\documentclass{article}

\usepackage{hyperref}
\usepackage[backend=biber]{biblatex}

\begin{document}
	A Kalmia client like Kalmium with builtin AI.
	
	This project is in development. Builtin AI is just a test and will be removed in the future. 
	
	FCWSLIB is also its own project, this will not be merged into Kalmium for the foreseeable future.
	
	\part{Install}
	
	\section{Install a tool for installing Python packages}
	
	\subsection{Conda}
	
	\subsubsection{Arch Linux}
	
	Install\footnote{\url{https://wiki.archlinux.org/title/Help:Reading\#Installation\_of\_packages}} one of the following packages.
	
	\begin{enumerate}
		\item anaconda\footnote{\url{https://github.com/archlinuxcn/repo/tree/master/archlinuxcn/anaconda}}\textsuperscript{CNRepo}
		\item miniconda\footnote{\url{https://github.com/archlinuxcn/repo/tree/master/archlinuxcn/miniconda}}\textsuperscript{CNRepo}
		\item python-conda\footnote{\url{https://aur.archlinux.org/packages/python-conda}}\textsuperscript{CNRepo}
		\item miniconda3\footnote{\url{https://aur.archlinux.org/packages/miniconda3}}\textsuperscript{CNRepo}
		\item anaconda\footnote{\url{https://aur.archlinux.org/packages/anaconda}}\textsuperscript{CNRepo}
	\end{enumerate}
	
	\subsection{PIP}
	
	Install\footnote{\url{https://wiki.archlinux.org/title/Help:Reading\#Installation\_of\_packages}} python-pip\footnote{\url{https://archlinux.org/packages/extra/any/python-pip}} package.
	
	Befero using the Arch Linux CN repository.
	
	conda install conda-forge::pyside6
	conda install conda-forge::qt6-wayland
	conda install conda-forge::qt6-3d

	cd assets
	pyside6-rcc resources.qrc -o resources.py
	
	Move to Kalmium.
	
\end{document}
